Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-30 paper.tex
New results and changes in experiments
Several things to be done in 'TO DOs' along the text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

@@

@@

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & Input/Output\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

@@

In the first experiment, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\tabularnewline
\hline
M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\tabularnewline
\hline 
Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\tabularnewline
\hline 
Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\tabularnewline
\hline 
SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}
\end{table}

***TODO***: the results show...

@@

The selected features per method are shown in Table \ref{tab:features_selected}.

\begin{table}
\caption{Features selected by each method 
\label{tab:features_selected}}
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
No. & Feature & ReliefFAttributeEva & CfsSubsetEval & SOM\tabularnewline
\hline 
1 & ret\_price & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
2 & subject1 & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
\hline 
3 &  Editorial+Collection &  &  & \tabularnewline
\hline 
4 & binding &  &  & \tabularnewline
\hline 
5 & gifts & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
6 & distrib\_novelty & $\checkmark$ &  & \tabularnewline
\hline 
7 & tot\_points\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
8 & tot\_points\_sale\_1st\_year & $\checkmark$ &  & \tabularnewline
\hline 
9 & weeks\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
10 & print\_run & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
\hline 
\end{tabular}
\end{table}

% Antonio - TODO: change the names (and font format) to the same as variables in previous tables

*************** TO CHANGE WITH THE NEW RESULTS **************

\subsection{Obtained results}

% datasets:
%  original (16 vars)
%  4 vars
%  9 vars
%  SOM selected vars

Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the original dataset,
using the 16 variables that describe each book.
In this dataset, every book is described using not only numerical variables, 
but also two additional categorical variables, \emph{editorial} and \emph{collection}, 
which could, a priori, make harder to process the instances and build the different models.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
% OK
\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting
methods on the original dataset (16 variables per book). In this case,
due to the categorical variables, the MLP could not be run.}
\label{tabla:resultsT}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Base & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
\hline 
\hline 
M5P & 0.9076 & \textbf{202.1547} & 591.0257 & \textbf{35.31}\% & 42.10\% & 39.73\tabularnewline
\hline 
LR & 0.9204 & 255.0526 & 548.0975 & 44.5527 & 39.10\% & 0.03\tabularnewline
\hline 
SVM & \textbf{0.9402} & 203.4416 & \textbf{481.7528} & 35.54\% & \textbf{34.37}\% & 308.31\tabularnewline
\hline 
kNN & 0.7273 & 310.4078 & 993.2663 & 54.22\% & 70.85\% & 0\tabularnewline
\hline 
MLP & 0.9197 & 289.7393 & 585.6445 & 50.61\% & 41.78\% & 82.08\tabularnewline
\hline 
\end{tabular}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting methods
on the dataset obtained using the SOM feature selection method (6 variables
per book).}
\label{tabla:resultsSOM}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Base  & Correlation coefficient (\%)  & MAE  & RMSE  & RAE(\%)  & RRSE (\%)  & Time(sec)\tabularnewline
\hline 
\hline 
M5P  & 0.9161 & \textbf{198.8864} & 562.2113 & \textbf{34.74}\% & 40.11\% & 0.76\tabularnewline
\hline 
LR  & 0.9179 & 263.1702 & 556.3372 & 45.97\% & 39.69\% & 0.07\tabularnewline
\hline 
SVM  & \textbf{0.9388} & 207.7159 & \textbf{486.8913} & 36.28\% & \textbf{34.73}\% & 157.87\tabularnewline
\hline 
kNN  & 0.9304 & 202.0939 & 525.4642 & 35.30\% & 37.48\% & 0\tabularnewline
\hline 
MLP  & 0.9193 & 305.78 & 590.8412 & 53.41\% & 42.15\% & 25.83\tabularnewline
\hline 
\end{tabular}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 8 variables per book (obtained 
using the ReliefFAttributeEval feature selection method) can be shown 
in Table \ref{tabla:results9}.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task.

\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting methods
on the dataset obtained using the ReliefFAttributeEval feature selection method (8
variables per book).}
\label{tabla:results9}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
RAE & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
\hline 
\hline 
M5P & 0.9131 & \textbf{197.2886} & 580.328 & \textbf{34.46}\% & 41.40\% & 0.74\tabularnewline
\hline 
LR & 0.9209 & 254.3979 & 546.3899 & 44.44\% & 38.98\% & 0.03\tabularnewline
\hline 
SVM & \textbf{0.9394} & 204.2075 & \textbf{484.2617} & 35.67\% & \textbf{34.54}\% & 232.99\tabularnewline
\hline 
kNN & 0.9103 & 222.0827 & 597.8885 & 38.79\% & 42.65\% & 0\tabularnewline
\hline 
MLP & 0.9199 & 296.3581 & 575.9623 & 51.77\% & 41.09\% & 32.52\tabularnewline
\hline 
\end{tabular}
\end{table*}

Finally, obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 4 variables per book (obtained 
using the CfsSubsetEval feature selection method) can be shown 
in Table \ref{tabla:results4}.
As in the previous case, in this dataset every book is described using numerical 
variables. Thus, due to the number of features per book, building the different 
models is faster than in the previous cases.

\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting methods
on the dataset obtained using the CfsSubsetEval feature selection method (4 variables
per book).}
\label{tabla:results4}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
CFS & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
\hline 
\hline 
M5P & 0.9255 & \textbf{206.6638} & 531.306 & \textbf{36.10}\% & 37.90\% & 0.56\tabularnewline
\hline 
LR & 0.9194 & 259.3791 & 551.2005 & 45.31\% & 39.32\% & 0.05\tabularnewline
\hline 
SVM & \textbf{0.9342} & 213.0254 &\textbf{ 502.4048} & 37.21\% & \textbf{35.84}\% & 70.12\tabularnewline
\hline 
kNN & 0.9285 & 220.6548 & 527.7374 & 38.54\% & 37.65\% & 0\tabularnewline
\hline 
MLP & 0.9047 & 369.3486 & 646.1241 & 64.52\% & 46.09\% & 10.93\tabularnewline
\hline 
\end{tabular}
\end{table*}

In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models. 
Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method. In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%. 
Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively. 
According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p.eps}  &
\includegraphics[scale=0.22]{lr.eps}   &
\includegraphics[scale=0.22]{svm.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn.eps}  &
\includegraphics[scale=0.22]{mlp.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
  models.}
% You should use a log-log scale here to see it more clearly. Besides,
% please say in a comment the script you are using to generate it, we
% are going to need it later on - JJ
\label{conv2}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_RAE.eps}  &
\includegraphics[scale=0.22]{lr_RAE.eps}   &
\includegraphics[scale=0.22]{svm_RAE.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_RAE.eps}  &
\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
\label{conv2ReliefAttributeEval}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_CFS.eps}  &
\includegraphics[scale=0.22]{lr_CFS.eps}   &
\includegraphics[scale=0.22]{svm_CFS.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_CFS.eps}  &
\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
\label{conv2CfsSubsetEval}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p_SOM.eps}  &
\includegraphics[scale=0.22]{lr_SOM.eps}   &
\includegraphics[scale=0.22]{svm_SOM.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn_SOM.eps}  &
\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
\label{conv2SOM}
\end{figure*}

@@

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
using those categorical variables as part of a big dataset makes the problem 
hard to solve, both in required time to build the forecasting models as well as 
in the obtained errors.
Moreover, some methods are unable to build the models in a reasonable time.
%However, as stated before, Trevenque expert sales manager, taking into account 
%his knowledge in industry experience and their perceptions, decided that 
%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
Moreover, in these experiments it has been seen the difficulty to process 
information related to categorical variables, such as \emph{editorial} and 
\emph{collection}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
***TO DO***: rewrite this considering the new contents and results\\

When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

***TO DO***: complete this considering the new contents and results\\

@@

***TO DO***: rewrite this considering the new structure of the paper\\

@@

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

@@

In the first experiment, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered, also including the categorical ones, which make harder to process the instances and build the different models. SVM for instance, must previously transform these categories into numbers in order to deal with the data, which means the creation of a different (and new) variable per possible value. Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
% Antonio - Sam, verify this, please

Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
%{\scriptsize
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & Corr. coeffic  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\\
\hline
K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\\
\hline 
Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\\
\hline 
Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\\
\hline 
SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\\
\hline 
\end{tabular}
%}
\end{table}

***TODO***: Revise and fix the following text...

Moreover, in these experiments it has been seen the difficulty to process 
information related to categorical variables, such as \emph{editorial} and 
\emph{collection}.

@@

The selected features per method are shown in Table \ref{tab:features_selected}. Logically, just the independent or input variables are considered.

\begin{table}
\caption{Input features/variables selected by each method
\label{tab:features_selected}}
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
\hline 
1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
\hline 
2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
3 &  \texttt{collection} &  &  & \\
\hline 
4 & \texttt{binding} &  &  & \\
\hline 
5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
\hline 
6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
\hline 
7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
\hline 
9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
\end{tabular}
\end{table}

Thus, we have run the same experiments as in Section \ref{subsec:results_all_editors} with the whole dataset (all the editors), but considering the selected features by each method. The results are shown in Table

\begin{table}

\centering{}%
\caption{Predicting Total sales for all editors based on features selected
by each method.
\label{tab:results_all_editors_fs}}

% RELIEFATTRIBUTEEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.892 $\pm$0.102 & 211.147 $\pm$22.41 & 616.347 $\pm$321.254 & 36.928 $\pm$3.414 & 47.299 $\pm$26.827 & 0.4906 $\pm$0.0223\\
\hline 
K-NN & 0.869 $\pm$0.087 & 231.782 $\pm$24.246 & 668.028 $\pm$205.135 & 40.483 $\pm$3.058 & 51.276 $\pm$16.807 & 0.0015 $\pm$0.0042\\
\hline 
Random Forest & 0.91 $\pm$0.048 & 198.16 $\pm$19.499 & 589.353 $\pm$195.801 & 34.61 $\pm$2.27 & 44.209 $\pm$11.634 & 3.633 $\pm$0.2039\\
\hline 
Linear Regression & 0.864 $\pm$0.081 & 346.875 $\pm$25.395 & 695.897 $\pm$242.49 & 60.754 $\pm$4.549 & 53.164 $\pm$19.432 & 0.0124 $\pm$0.0072\\
\hline 
SVM & 0.842 $\pm$0.039 & 252.868 $\pm$33.384 & 858.26 $\pm$318.225 & 44.012 $\pm$3.038 & 62.22 $\pm$7.148 & 38.9667 $\pm$5.7518\\
\hline 
\end{tabular}

% CFSSUBEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.873 $\pm$0.09 & 266.777 $\pm$23.117 & 662.319 $\pm$245.272 & 46.66 $\pm$3.247 & 50.9 $\pm$20.35 & 0.4103 $\pm$0.0428\\
\hline 
K-NN & 0.84 $\pm$0.099 & 289.092 $\pm$22.834 & 743.917 $\pm$260.45 & 50.591 $\pm$3.496 & 57.301 $\pm$22.899 & 0.001 $\pm$0.0006\\
\hline 
Random Forest & 0.85 $\pm$0.106 & 278.417 $\pm$23.073 & 714.134 $\pm$278.654 & 48.713 $\pm$3.434 & 55.264 $\pm$24.412 & 2.479 $\pm$0.1264\\
\hline 
Linear Regression & 0.859 $\pm$0.062 & 356.35 $\pm$22.43 & 708.056 $\pm$195.145 & 62.423 $\pm$4.216 & 53.974 $\pm$14.053 & 0.0067 $\pm$0.0009\\
\hline 
SVM & 0.86 $\pm$0.063 & 288.474 $\pm$30.322 & 817.562 $\pm$253.237 & 50.302 $\pm$2.375 & 60.266 $\pm$5.675 & 32.7252 $\pm$5.7438\\
\hline
\end{tabular}\\

% SOM
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\\
\hline
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.866 $\pm$0.104 & 234.091 $\pm$23.186 & 699.563 $\pm$317.196 & 40.924 $\pm$3.248 & 53.698 $\pm$26.867 & 0.4754 $\pm$0.1228\\
\hline 
K-NN & 0.868 $\pm$0.086 & 237.91 $\pm$25.344 & 665.639 $\pm$212.05 & 41.547 $\pm$3.141 & 50.96 $\pm$16.721 & 0.0009 $\pm$0.0035\\
\hline 
Random Forest & 0.898 $\pm$0.051 & 211.867 $\pm$20.072 & 617.776 $\pm$187.155 & 37.017 $\pm$2.461 & 46.581 $\pm$11.144 & 2.932 $\pm$0.1083\\
\hline 
Linear Regression & 0.855 $\pm$0.075 & 351.993 $\pm$23.72 & 714.756 $\pm$214.213 & 61.65 $\pm$4.278 & 54.665 $\pm$16.881 & 0.0113 $\pm$0.0074\\
\hline 
SVM & 0.845 $\pm$0.035 & 267.706 $\pm$33.819 & 888.331 $\pm$308.932 & 46.604 $\pm$2.865 & 64.62 $\pm$5.445 & 32.2689 $\pm$4.7404\\
\hline 
\end{tabular}

\end{table}

***TO DO***: comment the results

***TO DO***: Think if including the graphs (scatter plots).

%In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models. 
%Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
%Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method. In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%. 
%Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively. 
%According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
%On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p.eps}  &
%\includegraphics[scale=0.22]{lr.eps}   &
%\includegraphics[scale=0.22]{svm.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn.eps}  &
%\includegraphics[scale=0.22]{mlp.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
%  models.}
% You should use a log-log scale here to see it more clearly. Besides,
% please say in a comment the script you are using to generate it, we
% are going to need it later on - JJ
%\label{conv2}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_RAE.eps}  &
%\includegraphics[scale=0.22]{lr_RAE.eps}   &
%\includegraphics[scale=0.22]{svm_RAE.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_RAE.eps}  &
%\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
%\label{conv2ReliefAttributeEval}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_CFS.eps}  &
%\includegraphics[scale=0.22]{lr_CFS.eps}   &
%\includegraphics[scale=0.22]{svm_CFS.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_CFS.eps}  &
%\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
%\label{conv2CfsSubsetEval}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_SOM.eps}  &
%\includegraphics[scale=0.22]{lr_SOM.eps}   &
%\includegraphics[scale=0.22]{svm_SOM.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_SOM.eps}  &
%\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
%\label{conv2SOM}
%\end{figure*}

@@

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
%Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
%\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4},
%using those categorical variables as part of a big dataset makes the problem 
%hard to solve, both in required time to build the forecasting models as well as 
%in the obtained errors.

%Moreover, some methods are unable to build the models in a reasonable time.
%However, as stated before, Trevenque expert sales manager, taking into account 
%his knowledge in industry experience and their perceptions, decided that 
%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

\section{Example Cases}
\label{example_cases}

This section will present some experiments conducted on the data concerning four different example cases, namely:
\begin{itemize}
    \item best seller editorial
    \item medium seller editorial
    \item best varied editorial
    \item medium varied editorial
\end{itemize}

***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).

\subsection{Sales forecasting with all pre-sales features}
\label{subsec:case_sales_all_features}

Case 1-A: Developing prediction models to predict Total sales for
Editor704 (An editor with the most number of different books sold) - 293
instances.

\begin{table}
\caption{Predicting Total sales for Editor704}
